---
title: "case_study"
output: html_document
date: "2023-10-10"
---

```{r}
library(tidyverse)
library(ggridges)
```


## Get the data: 
```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location / 2)
```


## Brainstorm questions

- Where are AirBNBs expensive? 
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? What about rating?
- How long are AirBNBs active? 
  - Are AirBNBs illegal and do they shut down?
- Which units have the most availbility?
- How is review score impacted by location? 
- How many apartments are run by one host? 
  - Does that affect price? 
  - Does that vary by neighborhood? 
- What are AirBNBs? 
  _ Lat and Long

## Code to answer questions (solo)
```{r}
# How many AirBNBs are in each borough 
nyc_airbnb |> 
  group_by(borough) |> 
  summarize(n_obs = n())

# How many AirBNBs are iin each borough by room type 
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(n_obs = n())

```
 
## Do some EDA with class 
```{r}
nyc_airbnb |> 
  count(borough)
```

```{r}
#can do this for mean or median to compare them 
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type, 
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange(desc(mean_price)
  )
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```

## Try to make a map 
```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

```{r}
library(leaflet)

nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  slice_sample(n = 500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~long, ~lat, radius = 0.5)
```

